---
title: "DATA604 - Week8"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**PACKAGES**

```{r, echo=TRUE,message=FALSE, warning=FALSE}
library(fitdistrplus)
library(MASS)
library(httr)
library(DiscreteInverseWeibull)
```

**DATA SOURCES**

```{r, echo=TRUE, message=FALSE, warning=FALSE}

data1 <- "https://raw.githubusercontent.com/Misterresearch/DATA604/master/Problem_Dataset_06_01.csv"

data2 <- "https://raw.githubusercontent.com/Misterresearch/DATA604/master/Problem_Dataset_06_02.csv"

data3 <- "https://raw.githubusercontent.com/Misterresearch/DATA604/master/Problem_Dataset_06_03.csv"

dataTB1 <- read.csv(file = data1, header = FALSE, sep = ',', na.strings = "NA")
dataTB2 <- read.csv(file = data2, header = FALSE, sep = ',', na.strings = "NA")
dataTB3 <- read.csv(file = data3, header = FALSE, sep = ',', na.strings = "NA")

```

**DISTRIBUTION PLOTS & RECOMMENDATION Q1-3**

Kelton Chapter6, Q1-3. Please see the plots of the interarrival times for each data set, as well as the recommendation for best distribution - followed by the appropriate Simio setting.

Q1 - (see below),

criteria #1 - continuous
criteria #2 - Asymetric
crtiteria # - all positive

Recommendation: Exponential Distribution
Simio expression: Random.Exponential(.083)

Q2 - (see below),

criteria #1 - continuous
criteria #2 - Asymetric
crtiteria # - some positive

Recommendation: Weibull
Simio expression:Random.Weibull(1.88 , 12.36)


Q3 - (see below),

criteria #1 - discreter
criteria #2 - Asymetric
crtiteria # - all positive

Recommendation: Geometric
Simio expression: Random.Geometric(.25)

```{r,echo=TRUE, message=FALSE, warning=FALSE}

plotdist(dataTB1$V1, histo = TRUE, demp = TRUE)
fitdist(dataTB1$V1, distr = "exp", method = c("mle","mme", "qme", "mge"), start=NULL, fix.arg = NULL, discrete = FALSE, keepdata = TRUE)

plotdist(dataTB2$V1, histo = TRUE, demp = TRUE)
fitdist(dataTB2$V1, distr = "weibull", method = c("mle","mme", "qme", "mge"), start=NULL, fix.arg = NULL, discrete = FALSE, keepdata = TRUE)

plotdist(dataTB3$V1, histo = TRUE, demp = TRUE)
fitdistr(dataTB3$V1, "geometric")
```

**DISTRIBUTION PLOTS & RECOMMENDATION Q4 & 5**


```{r, echo=TRUE, warning=FALSE, message=FALSE}

#solution for Q4
qnorm(runif(20))

#soultion for q5
q <- .6
beta <- 3
x <-1:40
ahrdiweibull(x, q, beta)

```



Sources:

[Distribution choices](https://2.bp.blogspot.com/-SpjgitfNMb0/TteevRR_Y2I/AAAAAAAAAFQ/IZgd32z2AI8/s1600/distributions.png)

[Fitting distributions with R](https://www.r-bloggers.com/fitting-distributions-with-r/)

[MASS::fitdistr](https://stat.ethz.ch/R-manual/R-devel/library/MASS/html/fitdistr.html)

[CDF](http://www.r-tutor.com/elementary-statistics/probability-distributions/continuous-uniform-distribution)

[simulation by inverse cdf](https://www.r-bloggers.com/simulation-by-inverse-cdf/)


